---
title: ""
output: html_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

library(tidyverse)
library(gtsummary)
library(survey)

# temp <- readRDS("Temp020525.RDA")
```

# `r params$outcome_label`

## Frequency Plot 

```{r}
generate_plot(temp2, params$outcome, params$outcome_label)
```

## Demographics Table (Unweighted)

```{r}
tbl1_unweighted(temp, params$outcome)
```

## Demographics Table (Weighted)

```{r message=TRUE, warning=TRUE, eval= F}
tbl1_weighted(desg_, params$outcome)
```

2015 - 2019

```{r message = TRUE, warning=TRUE}
tbl1_weighted_alt(desg_1, params$outcome)
```

2021 - 2023

```{r message=TRUE, warning=TRUE}
tbl1_weighted_alt(desg_2, params$outcome)
```

## Model 0 

(Unweighted/Unadjusted Table)

```{r}
obj0 = lapply(substance_list[1:18], ud_regress, datsrc = grp_ )


unadj_temp = bind_rows(lapply(obj0, function(x) x$table_body)) %>% 
  select(N_event, var_label, N_obs, estimate, ci, p.value)

unadj_temp %>% 
  select(Var = var_label, Estimate = estimate, CI = ci, p = p.value) %>% 
  knitr::kable(digits = 3)

rm(obj0, unadj_temp)
```

(Classic Hallucinogens ~ Weighted)

### 2015 - 2019 
```{r, warning=FALSE}
# 2015 - 2019
use_regress_b(params$outcome, "halluc_p")
```

### 2021 - 2023
```{r, warning=FALSE}
# 2021 - 2023
use_regress_a(params$outcome, "halluc_p")
```

```{r, warning=FALSE}
m1vars = "catag6 + race_cat + income + irsex + eduhighcat + mj_ever + stm_ever+ trq_ever + inh_ever + sed_ever + coc_ever + meth_ever"
m2vars = str_c(m1vars, " + difobtlsd + difobther")
m3vars = str_c(m1vars, " + factor(region_1)")

m1varsmj = "catag6 + race_cat + income + irsex + eduhighcat + stm_ever+ trq_ever + inh_ever + sed_ever + coc_ever + meth_ever"
m2varsmj = str_c(m1varsmj, " + difobtlsd + difobther")

psyvars = "psilcy_ever + peymesc + lsd_ever + dmt_ever"
```

## Model 1

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use* 

### 2015 - 2019 
```{r, warning = F}
# 2015 - 2019
use_regress_b(params$outcome,paste("halluc_p" ," + "  , m1vars))
```

### 2021 - 2023
```{r, warning = F}
# 2021 - 2023
use_regress_a(params$outcome, paste("halluc_p" ," + "  , m1vars))
```

### 2015 - 2019 
```{r, warning = F}
# 2015 - 2019
use_regress_b(params$outcome, paste(psyvars, " + "  , m1vars))
```

### 2021 - 2023
```{r, warning = F}
# 2021 - 2023
ud_regress_a(paste(psyvars, " + "  , m1vars))
```

Model 2 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Difficulty Obtaining* 

### 2015 - 2019 
```{r}
# 2015 - 2019
use_regress_b(params$outcome, paste("halluc_p" ," + "  , m2vars))
```

### 2021 - 2023
```{r}
# 2021 - 2023
use_regress_a(params$outcome, paste("halluc_p" ," + "  , m2vars))
```

### 2015 - 2019
```{r}
# 2015 - 2019
use_regress_b(params$outcome, paste(psyvars ," + "  , m2vars))
```

### 2021 - 2023
```{r}
### 2021 - 2023
use_regress_a(params$outcome, paste(psyvars ," + "  , m2vars))
```

Model 3 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Geo Region* 

### 2015 - 2019
```{r, eval = FALSE }
# 2015 - 2019
use_regress_b(params$outcome, paste("halluc_p" ," + "  , m3vars))
```

### 2021 - 2023
```{r, eval = FALSE }
# 2021 - 2023
use_regress_a(params$outcome, paste("halluc_p" ," + "  , m3vars))
```

### 2015 - 2019
```{r, eval = FALSE }
# 2015 - 2019
use_regress_b(params$outcome, paste(psyvars ," + "  , m3vars))
```

### 2021 - 2023
```{r, eval = FALSE }
# 2021 - 2023
use_regress_a(params$outcome, paste(psyvars ," + "  , m3vars))
```

Model 4 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Policy 2019/2023* 

### 2015 - 2019
```{r, eval = FALSE }
# 2015 - 2019
use_regress_b(params$outcome, paste("halluc_p" ," + "  , m1vars, " + " , policy19))
```

### 2021 - 2023
```{r, eval = FALSE }
# 2021 - 2023
use_regress_a(params$outcome, paste("halluc_p" ," + "  , m1vars, " + ",  policy23))
```

### 2015 - 2019
```{r, eval = FALSE }
# 2015 - 2019
use_regress_b(params$outcome, paste(psyvars ," + "  , m1vars, " + " , policy19))
```

### 2021 - 2023
```{r, eval = FALSE }
# 2021 - 2023
use_regress_a(params$outcome, paste(psyvars ," + "  , m1vars, " + ",  policy23))
```
