---
title: ""
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

library(tidyverse)
library(gtsummary)
library(survey)

# temp <- readRDS("Temp020525.RDA")
```

# `r params$outcome_label`

## Frequency Plot 

```{r}
generate_plot(temp2, params$outcome, params$outcome_label)
```

## Demographics Table (Unweighted)

```{r}
tbl1_unweighted(temp, params$outcome)
```

## Demographics Table (Weighted)

```{r message = TRUE, warning=TRUE, eval = F}
tbl1_weighted(desg_, params$outcome)
```

2015 - 2019

```{r message = TRUE, warning=TRUE}
tbl1_weighted_alt(desg_1, params$outcome)
```

2021 - 2023

```{r message = TRUE, warning=TRUE}
tbl1_weighted_alt(desg_2, params$outcome)
```


### Frequency Plot 

```{r}
generate_plot(temp2, params$outcome, params$outcome_label)
```

### Demographics by Cannabis Use Disorder

```{r}
tbl1_unweighted(grp_, params$outcome)
tbl1_weighted(desg_, params$outcome)
```

## Model 0

(Classic Hallucinogens ~ Weighted)

### 2015 - 2019 
```{r}
# 2015 - 2019
use_regress_b(params$outcome, paste("halluc_p"))
```

### 2021 - 2023
```{r}
# 2021 - 2023
use_regress_a(params$outcome, paste("halluc_p"))
```

## Model 1

```{r}
use_regress_b(params$outcome, paste("halluc_p", " + ", m1varsmj))
use_regress_a(params$outcome, paste("halluc_p", " + ", m1varsmj))
```

## Model 2 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Difficulty Obtaining* 

### 2015 - 2019 
```{r}
# 2015 - 2019
use_regress_b(params$outcome, paste("halluc_p", " + ", m2varsmj))
```

### 2021 - 2023 
```{r}
# 2021 - 2023
use_regress_a(params$outcome, paste("halluc_p", " + ", m2varsmj))
```

## Model 3 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Geo Region* 

### 2015 - 2019
```{r, eval = FALSE }
# 2015 - 2019
use_regress_b(params$outcome, paste("halluc_p", " + ", m3varsmj))
```

### 2021 - 2023 
```{r, eval = FALSE }
# 2021 - 2023
use_regress_a(params$outcome, paste("halluc_p", " + ", m3varsmj))
```

## Model 4

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Policy 2019/2023* 

### 2015 - 2019
```{r, eval = FALSE}
# 2015 - 2019
use_regress_b(params$outcome, paste("halluc_p", " + ", m1varsmj, " + ", policy19))
```

### 2021 - 2023 
```{r, eval = FALSE}
# 2021 - 2023
use_regress_a(params$outcome, paste("halluc_p", " + ", m1varsmj, " + ", policy23))
```
