---
title: "NSDUH Outcome Reports"
author: '@naddo'
date: !r Sys.Date()
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

library(tidyverse)
library(gtsummary)
library(survey)

temp <- readRDS("~/Library/CloudStorage/Box-Box/Emergency Medicine 2024/CUPS3_OUD/Temp020525.RDA")
source("02_tools.R")
source("PolicyLabels.R")
```

```{r}
temp2 <- temp %>% haven::zap_labels() 

# Adds Simulated Region !!! NOT FOR USE!!! 
df <- tibble(region_1 = 1:4)
region_d <- sample_n(df, length(temp2$year), replace = TRUE)

temp2 <- bind_cols(temp2, region_d) %>% 
  mutate(
    race_cat = factor(race_cat) %>% fct_relevel(.,"NH White", after = 0L)
    )


grp_ <- temp2  %>% filter(!catag6=="") %>% filter(!year == 2020) %>% droplevels() %>% 
  mutate(
    race_cat = factor(race_cat) %>% fct_relevel(.,"NH White", after = 0L)
    )

grp1 <- temp2 %>% filter(year > 2020) %>% filter(!catag6 == "")
grp2 <- temp2 %>% filter(year < 2020) %>% filter(!catag6 == "")

desg_ <-
  temp2 %>% haven::zap_labels() %>% filter(!catag6 == "") %>% droplevels() %>%
  svydesign(id      = ~verep,
            strata  = ~vestr_,
            weights = ~psnwt,
            data    = . , nest = T)


desg_1 <-
  temp2 %>% haven::zap_labels() %>% filter(!catag6 == "") %>% filter(year < 2020) %>%  droplevels()  %>%
  svydesign(id      = ~verep,
            strata  = ~vestr_,
            weights = ~psnwt,
            data    = . , nest = T)


desg_2 <-
  temp2 %>% haven::zap_labels() %>% filter(!catag6 == "") %>% filter(year > 2020) %>% droplevels() %>%
  svydesign(id      = ~verep,
            strata  = ~vestr_,
            weights = ~psnwt,
            data    = . , nest = T)

# Prepare survey design if needed
desg_ <- svydesign(
  id = ~verep,
  strata = ~vestr_,
  weights = ~psnwt,
  data = temp,
  nest = TRUE
)

substance_list <- c("halluc_p", "lsd_ever", "psilcy_ever", "ecstasy_ever", "ket_ever", "pcp_ever", "mesc_ever","peyote_ever","dmt_ever", "salv_ever","mj_ever", "coc_ever", "meth_ever", "stm_ever", "trq_ever", "inh_ever", "sed_ever", "herflag", "pnranyflag", "any_opi")

reference_summary <- function(data) {
  data %>%
  tbl_summary(
    include = all_of(substance_list),
    percent = "column",
    by = "year",
    label = c(outcome_list_label, substance_list_label)
  )
}
```

##  Reference Summary 

```{r}
reference_summary(temp2)
```

## Opioid Use Disorder 

```{r}
params = list(outcome = "opioid_use_f", outcome_label = "Opioid Use Disorder")

rmarkdown::render("01_ReportOUD.Rmd",
                  params = list(
                    outcome =  opioid_use_f,
                    outcome_label = "Opioid Use Disorder",
                    ),
                    output_format = rmarkdown::html_document(
                      title = "Past Year Opioid Use Disorder"
                      ),
                    output_file = "01ReportOUD.html",
                    output_dir = "OUD and Hallucinogen Reports/",
                    output_options = list(
                      pandoc_args = c("--metadata=title:\"Opioid Use Disorder\"")),
                    clean = TRUE
                  )
```

## Other Past Year Substance Use 

### Past Year Cannabis Use    

```{r}
params = list(outcome =  "mrjyr", outcome_label = "Past Year Cannabis Use")

rmarkdown::render("03ReportMJV.Rmd",
                  params = list(
                    outcome =  mrjyr,
                    outcome_label = "Past Year Cannabis Use",
                    ),
                    output_format = rmarkdown::html_document(
                      title = "Past Year Cannabis Use"
                      ),
                    output_file = "02ReportCannabis.html",
                    output_dir = "OUD and Hallucinogen Reports/",
                    output_options = list(
                      pandoc_args = c("--metadata=title:\"Past Year Cannabis Use\"")),
                    clean = TRUE
)
```

### Past Year Ketamine Use   
```{r}
params = list(outcome = "ketminyr", outcome_label = "Past Year Ketamine Use")

rmarkdown::render("01_ReportOUD.Rmd",
                  params = list(
                    outcome =  ketminyr,
                    outcome_label = "Past Year Ketamine Use",
                    ),
                    output_format = rmarkdown::html_document(
                      title = "Past Year Ketamine Use"
                      ),
                    output_file = "03ReportKetamine.html",
                    output_dir = "OUD and Hallucinogen Reports/",
                    output_options = list(pandoc_args = c("--metadata = title:\"Past Year Ketamine Use\"")),
                    clean = TRUE
)
```

### Past Year MDMA Use    
```{r}
params = list(outcome = "ecstmoyr", outcome_label = "Past Year MDMA Use")

rmarkdown::render("01_ReportOUD.Rmd",
                  params = list(
                    outcome =  ecstmoyr,
                    outcome_label = "Past Year MDMA Use"
                    ),
                    output_format = rmarkdown::html_document(
                      title = "Past Year MDMA Use"
                    ),
                    output_file = "04ReportMDMA.html",
                    output_dir = "OUD and Hallucinogen Reports/",
                    output_options = list(
                      pandoc_args = c("--metadata=title:\"Past Year MDMA Use\"")
                    ),
                    clean = TRUE
                  )
```

### Past Year Cocaine Use
```{r}
params = list(outcome = "cocyr", outcome_label = "Past Year Cocaine Use")

rmarkdown::render("01_ReportOUD.Rmd",
                  params = list(
                    outcome =  py,
                    outcome_label = "Past Year Cocaine Use",
                    ),
                    output_format = rmarkdown::html_document(
                      title = "Past Year Cocaine Use"
                    ),
                    output_file = "11ReportCocaine.html",
                    output_dir = "OUD and Hallucinogen Reports/",
                    output_options = list(
                      pandoc_args = c("--metadata=title:\"Past Year Non Prescribed Stimulant Use\"")
                    ),
                    clean = TRUE
)
```

### Past Year Methamphetamine Use
```{r}
params = list(outcome = "methamyr", outcome_label = "Past Year Methamphetamine Use")

rmarkdown::render("01_ReportOUD.Rmd",
                  params = list(
                    outcome =  py,
                    outcome_label = "Past Year Methamphetamine Use",
                    ),
                    output_format = rmarkdown::html_document(
                      title = "Past Year Methamphetamine Use"
                    ),
                    output_file = "10ReportMeth.html",
                    output_dir = "OUD and Hallucinogen Reports/",
                    output_options = list(
                      pandoc_args = c("--metadata=title:\"Past Year Non Prescribed Stimulant Use\"")
                    ),
                    clean = TRUE
)
```


### Past Year Non Prescribed Stimulant Use
```{r}
params = list(outcome = "py_cocmeth", outcome_label = "Past Year Non Prescribed Stimulant Use")

rmarkdown::render("01_ReportOUD.Rmd",
                  params = list(
                    outcome =  py_cocmeth,
                    outcome_label = "Past Year Non Prescribed Stimulant Use",
                    ),
                    output_format = rmarkdown::html_document(
                      title = "Past Year Non Prescribed Stimulant Use"
                    ),
                    output_file = "05ReportStim.html",
                    output_dir = "OUD and Hallucinogen Reports/",
                    output_options = list(
                      pandoc_args = c("--metadata=title:\"Past Year Non Prescribed Stimulant Use\"")
                    ),
                    clean = TRUE
)
```

## Other Past Year Use Disorders 

### Alcohol Use Disorder    
```{r}
params = list(outcome =  "alc_use_f", outcome_label = "Alcohol Use Disorder" )

rmarkdown::render("01_ReportOUD.Rmd",
                  params = list(
                    outcome =  alc_use_f,
                    outcome_label = "Alcohol Use Disorder",
                    ),
                    output_format = rmarkdown::html_document(
                      title = "Alcohol Use Disorder"
                    ),
                    output_file = "06ReportAUD.html",
                    output_dir = "OUD and Hallucinogen Reports/",
                    output_options = list(
                      pandoc_args = c("--metadata=title:\"Alcohol Use Disorder\"")),
                    clean = TRUE
)
```

### Binge Alcohol use past 30 days
```{r}
params = list(outcome =  "binge_drink_f", outcome_label = "Binge Alcohol Use past 30 days" )

rmarkdown::render("01_ReportOUD.Rmd", 
                  params = list(
                    outcome =  binge_drink_f,
                    outcome_label = "Binge Alcohol Use past 30 days",
                    ),
                    output_format = rmarkdown::html_document(
                      title = "Binge Alcohol Use past 30 days"
                    ),
                    output_file = "07ReportBingeAlc.html",
                    output_dir = "OUD and Hallucinogen Reports/",
                    output_options = list(
                      pandoc_args = c("--metadata=title:\"Binge Alcohol Use past 30 days\"")
                    ),
                    clean = TRUE
)
```

### Non Prescribed Stimulant Use Disorder 
```{r}
params = list(outcome = "cocmeth_use_f", outcome_label = "Past Year Non Prescribed Stimulant Use Disorder")

rmarkdown::render("01_ReportOUD.Rmd",
                  params = list(
                    outcome =  cocmeth_use_f,
                    outcome_label = "Past Year Non Prescribed Stimulant Use Disorder",
                    ),
                    output_format = rmarkdown::html_document(
                      title = "Past Year Non Prescribed Stimulant Use Disorder"
                      ),
                    output_file = "08ReportStmUD.html",
                    output_dir = "OUD and Hallucinogen Reports/",
                    output_options = list(
                      pandoc_args = c("--metadata=title:\"Past Year Non Prescribed Stimulant Use Disorder\"")
                      ),
                    clean = TRUE
)
```

### Cannabis Use Disorder
```{r}
params = list(outcome = "mrj_use_f", outcome_label = "Past Year Cannabis Use Disorder")

rmarkdown::render("03ReportMJV.Rmd",
                  params = list(
                    outcome =  mrj_use_f,
                    outcome_label = "Past Year Cannabis Use Disorder",
                    ),
                    output_format = rmarkdown::html_document(
                      title = "Past Year Cannabis Use Disorder"
                      ),
                    output_file = "09ReportCUD.html",
                    output_dir = "OUD and Hallucinogen Reports/",
                    output_options = list(pandoc_args = c("--metadata=title:\"Past Year Cannabis Use Disorder\"")),
                    clean = TRUE
)
```
