---
title: "Psilocybin Policy"
output:
  word_document: default
  html_document: default
---

```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE)

library(tidyverse)
library(gtsummary)
library(survey)
```

```{r}
temp %>% select(year, halluc_ever) %>% table() # Missing

temp %>% select(year, hallucly) %>% table() # Missing
temp %>% select(year, psilcy2) %>% table()
temp %>% select(year, lsd_ever) %>% table()
temp %>% select(year, ecstasy_ever) %>% table()

# All Missing
temp %>% select(year, new_halluc) %>% table()
temp %>% select(year, new_psilocybin) %>% table()
temp %>% select(year, new_lsd) %>% table()
temp %>% select(year, new_nl_halluc) %>% table()

temp %>% select(year, lsdyr) %>% table()

temp %>% select(year, age_cat) %>% table()
temp %>% select(year, irsex) %>% table()
temp %>% select(year, income) %>% table()
temp %>% select(year, msa) %>% table()
temp %>% select(year, ins_cat) %>% table() 
temp %>% select(year, eduhighcat) %>% table()
```

```{r}
temp <- readRDS("Temp020525.RDA")
```


```{r utils}
# Variable Label Definitions file - to a source file
halluc_epi_label  = 
  list(
        halluc_ever = "CUPS Hallucinogen Ever", 
        hallucflag  = "NSDUH Hallucinogen Ever" , 
        halluc_p    = "'Classic' Hallucinogen Ever",
        psilcy_ever = "Psilocybin Ever", 
        psilcy_only = "Only Psilocybin Use", 
        new_psil = "New Psilocybin Use", 
        pastyr_psil2 = "Past Year Psilocybin Use", 
        pastyr_halluc = "Past Year Hallucinogen", 
        pastyr_lsd = "Past Year LSD", 
        pastyr_ecs = "Past Year Ecstasy"
        )

source("PolicyLabels.R")
oud_epi_label = outcome_list_label 

```

```{r}
temp %>%
  tbl_summary(
    include = all_of(halluc_epi_list[c(1:5, 7:10)]),
    label = c(halluc_epi_label),
    by = year) %>%
    add_overall()

```

```{r}
# Repeated Models
# Tests Use" by year and binary decriminalization
regress_0 <- function(df, outcome_var) {
  formula <- as.formula(paste(outcome_var,
    "~ syear + psil2d_bin"))
  glm(data = df, formula) %>%
    tbl_regression(
      estimate_fun = label_style_sigfig(digits = 4)
  ) %>% modify_column_unhide(columns = std.error)
}

# Tests Past Year Psilocybin Use" by year and binary decriminalization
# Adjusted - Age, Sex, Race + Educational Category + Insurance Category
regress_1 <- function(df, outcome_var) {
  formula <- as.formula(paste(outcome_var, 
  "~ syear + psil2d_bin + age_cat + irsex + race_cat + edu_cat + ins_cat + msa"))
  glm(data = df, formula) %>%
    tbl_regression(
      estimate_fun = label_style_sigfig(digits = 3)
  )
}

# Logistic regression for Use" by year and binary decriminalization
regress_3 <- function(df, outcome_var) {
  formula <- as.formula(paste(outcome_var,
  "~ syear + psil2d_bin"))
  glm(data = df, formula, family = binomial) %>% 
    tbl_regression(
      exponentiate = TRUE,
      estimate_fun = label_style_sigfig(digits = 4)
  ) %>% modify_column_unhide(columns = std.error)
}

# Logistic regression for Past Year Psilocybin Use" by year and binary decriminalization
# Adjusted - Age, Sex, Race + Educational Category + Insurance Category
regress_4 <- function(df, outcome_var) {
  formula <- as.formula(paste(outcome_var,
  "~ syear + psil2d_bin + age_cat + irsex + race_cat + edu_cat + ins_cat + msa"))
  glm(data = df, formula, family = binomial) %>%
    tbl_regression(
      exponentiate = TRUE,
      estimate_fun = label_style_sigfig(digits = 3)
  )
}
```

```{r}
# Tests Use" by year and binary decriminalization
regress_wt0 <- function(df, outcome_var) {
  formula <- as.formula(paste(outcome_var, "~ syear + psil2d_bin"))
  svyglm(data = df, formula, design = desg2_) %>%
    tbl_regression(
      estimate_fun = label_style_sigfig(digits = 4)
  ) %>% modify_column_unhide(columns = std.error)
}

# Tests Past Year Psilocybin Use" by year and binary decriminalization
# Adjusted - Age, Sex, Race + Educational Category + Insurance Category
regress_wt1 <- function(df, outcome_var) {
  formula <- as.formula(paste(outcome_var, "~ 
                              syear + psil2d_bin + age_cat + irsex + race_cat + edu_cat + ins_cat + msa"))
  svyglm(data = df, formula, design = desg2_) %>%
    tbl_regression(
      estimate_fun = label_style_sigfig(digits = 3)
  )
}

# Logistic regression for Use" by year and binary decriminalization
regress_wt3 <- function(df, outcome_var) {
  formula <- as.formula(paste(outcome_var, "~ syear + psil2d_bin"))
  svyglm(data = df, formula, family = quasibinomial, design = desg2_) %>%
    tbl_regression(
      exponentiate = TRUE,
      estimate_fun = label_style_sigfig(digits = 4)
  ) %>% modify_column_unhide(columns = std.error)
}

# Logistic regression for Past Year Psilocybin Use" by year and binary decriminalization
# Adjusted - Age, Sex, Race + Educational Category + Insurance Category
regress_wt4 <- function(df, outcome_var) {
  formula <- as.formula(paste(outcome_var,
  "~ syear + psil2d_bin + age_cat + irsex + race_cat + edu_cat + ins_cat + msa"))
  svyglm(data = df, formula, family = quasibinomial, design = desg2_) %>%
    tbl_regression(
      exponentiate = TRUE,
      estimate_fun = label_style_sigfig(digits = 3)
  ) %>% modify_column_unhide(columns = std.error) %>%
    add_overall() 
}
```

*Definitions:*

- Past Year Psilocybin:
    1 - New past year psilocybin use was inferred by combining variables reporting first ever hallucinogen use occurring within the past year and any lifetime use of psilocybin. 
    OR 
    2 - Past year hallucinogen use among people reporting no hallucinogen use other than psilocybin    
- New psilocybin use within the past year among previously hallucinogen-naïve participants and ii) lifetime psilocybin use. Control outcomes include past year MDMA and past year LSD use. 

- Decriminalization:
    Binary : Any Psilocyvin decrim in the
      2019  - on or after Jan 1, 2018  
      2020  - on or after Jan 1, 2019
      2021  - on or after Jan 1, 2020
      2022  - on or after Jan 1, 2021
      2023  - on or after Jan 1, 2022
      2024  - on or after Jan 1, 2023

```{r import, include = FALSE, warning = FALSE}
temp %>% group_by(year) %>% tally()
```

### Unweighted Substance Use in the Sample

Substance use Rates by Year (2013 - 2022)

```{r}
halluc_epi_list = attr(halluc_epi_label, "names")

temp %>% 
  tbl_summary(
    include = any_of(halluc_epi_list[c(1:5,7:9)]),
    label = c(halluc_epi_label),
    by = year
  ) %>% add_overall()
```

```{r}
mj_decriminalization = state_cannabis %>%
  filter(decriminalization == 1) %>%
  pull(st)

psilocybin_policy_ <- psilocybin_policy %>%
  mutate(
    fips_2 = str_sub(fips_5, 1, 2),
    effective_date = ymd(effective_date)
  )

psilocybin_policy2 <- psilocybin_policy %>%
  group_by(State, fips_2) %>% 
  summarise(effective = min(effective_date)) %>%
  ungroup() %>%
  mutate(psil_effective_year = year(effective))
```

```{r}
tmp2 = temp %>%
  # County Var
  # Use when State and County Available
  left_join(psilocybin_policy_ , by = c("fips5" = "STCTYCOD")) %>%
  # Use if only State Available
  # left_join(psilocybin_policy2, by = c("fips2" = "STUSABFIPS")) %>%
  mutate(
        # Assign Decriminalization Marijuana
        mjstate = if_else(state %in% mj_decriminalization, 1, 0),
        # Assign Decriminalization Psilocybin
        psil2d_bin = if_else(year >= psil_effective_year, 1, 0 , missing = 0),
         decriminalization = case_when(
          psil_effective_year <= 2019 ~ "Decrim 0",
          psil_effective_year <= 2020 ~ "Decrim 1",
          psil_effective_year <= 2021 ~ "Decrim 2",
          psil_effective_year <= 2022 ~ "Decrim 3",
          TRUE ~ "No Decrim"
        )) %>% filter(!is.na(catag6))
```

### Unweighted substance use vs decriminalization in Adults

<!--  Map Policy  -->
<!--  Map Psilocybin Substance Use  -->
  <!-- Hallucinogen Ever -->
  <!-- Psilocybin Ever -->
  <!-- Psilocybin in the last year -->
  <!-- OUD in the last year -->

```{r}
# dirtoken = ".../CUPS Population Study/NSDUH Data/Documentation/" 
# import1 <- sf::read_sf(str_c(dirtoken,"/Restricted Use Data/ShapeFile2018/SubstateRegionData161718.shp"))

# Continental  = import1[!import1$ST %in% c("AK","HI","PR"),]

# ggplot(Continental) +
# geom_sf(aes(fill = UDPYILA)) +
#   scale_colour_viridis_b(aesthetics = "fill", option ="viridis",direction = -1)+
#   theme_void() + labs(title = "Illicit Drug Use Disorder 2016-18")

# ggplot(Continental) +
# geom_sf(aes(fill = UDPYPNR)) +
#   scale_colour_viridis_b(aesthetics = "fill", option ="viridis",direction = -1)+
#   theme_void() + labs(title = "Pain Reliever Use Disorder 2016-18")

# ggplot(Continental) +
# geom_sf(aes(fill = ABODALC)) +
#   scale_colour_viridis_b(aesthetics = "fill", option ="viridis",direction = -1)+
#   theme_void() + labs(title = "Alcohol Use Disorder 2016-18")

# ggplot(Continental) +
# geom_sf(aes(fill = HERYR)) +
#   scale_colour_viridis_b(aesthetics = "fill", option ="viridis",direction = -1)+
#   theme_void() + labs(title = "Heroin use in the last year 2016-18")

# ggplot(Continental) +
# geom_sf(aes(fill = NEW_VARIABLE)) +
#   scale_colour_viridis_b(aesthetics = "fill", option ="viridis",direction = -1)+
#   theme_void() + labs(title = "New Variable Title")

```

### Test Decriminalization Variables 

- Compares Ever Decriminalization ever to Decrim by Calendar Year
```{r, eval =FALSE}
tmp2 %>% group_by(psil2d_bin) %>% tally()
```

- Compares Categorical Decriminalization against Calendar Year
```{r, eval =FALSE}
tmp2 %>% select(year, decriminalization) %>% table()
```

- Compares Ever Decriminalization to Categorical Decriminalization
```{r, eval =FALSE}
tmp2 %>% select(decriminalization, psil2d_bin) %>% table()
```

- Compares Ever Decrim by Calendar year to Categorical Decriminalization 
```{r, eval =FALSE}
tmp2 %>% select(decriminalization, psil2d_bin) %>% table()
```

### Weighted Data Structure
```{r}
# Weighted Set of Adult Respondents
# desg2_ <- desg_ %>% subset(!CATAG6=="")

tmp2 %>% droplevels() %>% haven::zap_labels() %>%
  svydesign(id      = ~verep,
            strata  = ~vestr_,
            weights = ~psnwt,
            data    = ., nest = T) -> desg2_
```

## Policy Manuscript Tables 

## Table 1. 

```{r, eval = FALSE}
tmp2 %>%
  select(age_cat,
         irsex,
         race_cat,
         edu_cat,
         currschool,
         ins_cat,
         income,
         msa, year
         ) %>%
  tbl_summary(by = year) %>% add_overall()
```

```{r, eval = FALSE}
tmp2 %>%
  select(age_cat,
         irsex,
         race_cat,
         edu_cat,
         currschool,
         ins_cat,
         income,
         msa, year, psil2d_bin
         ) %>%
  tbl_summary(by = psil2d_bin,
              label = list(
              age_cat = "Age Category",
              irsex = "Sex",
              edu_cat = "Education",
              ins_cat = "Insurance",
              income = "Income"
              ) %>%
  add_overall() %>%
  modify_header(label = "Variable",
              stat_0 = '**Overall**,\n N = {style_number(n, big.mark = ",")})',
              stat_1 = '**No local policy change**,\n
              N = {style_number(n, big.mark = ",")} ({style_percent(p)} )%',
              stat_2 = '**Decriminalized**,\n
              N = {style_number(n, big.mark = ",")} ({style_percent(p)} )%' )
```

Weighted Rates 

```{r, eval = FALSE}
desg2_ %>%
  tbl_svysummary(
    include = c(
      age_cat,
      irsex,
      race_cat,
      edu_cat,
      currschool,
      ins_cat,
      income,
      msa, year),
    by = year ) %>% add_overall()
```

```{r}
desg2_ %>% 
  tbl_svysummary(
    include = c(
      age_cat,
      irsex,
      race_cat,
      edu_cat,
      currschool,
      ins_cat,
      income,
      msa, year, psil2d_bin
    ),
    by = psil2d_bin,
    label = list(
    age_cat = "Age Category",
    irsex = "Sex",
    ins_cat = "Insurance",
    edu_cat = "Education",
    income = "Income"
              )
              ) %>% add_overall() %>%
  modify_header(
    label = "Variable",
    stat_0 = '**Overall**,\n N = {style_number(n, big.mark = ",")})', 
    stat_1 = '**No local policy change**,\n N = {style_number(n, big.mark = ",")} ({style_percent(p)} )%',
    stat_2 = '**Decriminalized**,\n  N = {style_number(n, big.mark = ",")} ({style_percent(p)} )%' 
    )
```

## Figure 1. 

```{r}
# Separate Figure Data and Plot

# Weight 
tmp2 %>% group_by(year, decriminalization) %>%
  summarize(rate_pastyrpsil = 100 * mean(pastyr_psil2), .groups = "keep") %>%
  mutate(Year = as.numeric(paste0(year)), `Past Year Psilocybin` = rate_pastyrpsil,
         decriminalization = fct_recode(decriminalization,
                                        `No Decrim` = "No Decrim",
                                        `Decrim 2019` = "Decrim 0",
                                        `Decrim 2020` = "Decrim 1",
                                        `Decrim 2021` = "Decrim 2",
                                        `Decrim 2022` = "Decrim 3"
                                        )) %>%
  ggplot(., aes(x = Year, y = `Past Year Psilocybin` , color=decriminalization)) +
    geom_line() + geom_point() +
    scale_y_continuous(limits = c(0.0,1.6), n.breaks = 12) +
    scale_x_continuous(n.breaks = 11) + theme_classic() + labs(color= "")
```

## Table 2.

### Unweighted - Overall

```{r}
tmp2 %>% regress_0("pastyr_psil2")
tmp2 %>% regress_1("pastyr_psil2")
tmp2 %>% regress_3("pastyr_psil2")
tmp2 %>% regress_4("pastyr_psil2")
```

### Weighted - Overall

```{r}
tmp2 %>% regress_wt0("pastyr_psil2")
tmp2 %>% regress_wt1("pastyr_psil2")
tmp2 %>% regress_wt3("pastyr_psil2")
tmp2 %>% regress_wt4("pastyr_psil2")
```

### Unweighted - Non-MJ States

```{r, eval = FALSE }
tmp2 %>% filter(mjstate == 0) %>% regress_0("pastyr_psil2")
tmp2 %>% filter(mjstate == 0) %>% regress_1("pastyr_psil2")
tmp2 %>% filter(mjstate == 0) %>% regress_3("pastyr_psil2")
tmp2 %>% filter(mjstate == 0) %>% regress_4("pastyr_psil2")
```

### Weighted - Non-MJ States

```{r, eval = FALSE}
tmp2 %>% filter(mjstate == 0) %>% regress_wt0("pastyr_psil2")
tmp2 %>% filter(mjstate == 0) %>% regress_wt1("pastyr_psil2")
tmp2 %>% filter(mjstate == 0) %>% regress_wt3("pastyr_psil2")
tmp2 %>% filter(mjstate == 0) %>% regress_wt4("pastyr_psil2")
```

### Unweighted - MJ States

```{r}
tmp2 %>% filter(mjstate == 1) %>% regress_0("pastyr_psil2")
tmp2 %>% filter(mjstate == 1) %>% regress_1("pastyr_psil2")
tmp2 %>% filter(mjstate == 1) %>% regress_3("pastyr_psil2")
tmp2 %>% filter(mjstate == 1) %>% regress_4("pastyr_psil2")
```

### Weighted - MJ States

```{r}
tmp2 %>% filter(mjstate == 1) %>% regress_wt0("pastyr_psil2")
tmp2 %>% filter(mjstate == 1) %>% regress_wt1("pastyr_psil2")
tmp2 %>% filter(mjstate == 1) %>% regress_wt3("pastyr_psil2")
tmp2 %>% filter(mjstate == 1) %>% regress_wt4("pastyr_psil2")
```


## Additional Variables 

```{r}
# For each variable, repeat the analyses

# PastYr HallucinogenUse
# PastYr LSD
# PastYr Mdma Use 
  
for (outcome_var in c("hallucly", "pastyr_lsd", "pastyr_ecs")) {
  cat("\n## Results for", outcome_var, "\n")
  
  # Unweighted - Overall
  tmp2 %>% regress_0(outcome_var)
  tmp2 %>% regress_1(outcome_var)
  tmp2 %>% regress_3(outcome_var)
  tmp2 %>% regress_4(outcome_var)
  
  # Weighted - Overall
  tmp2 %>% regress_wt0(outcome_var)
  tmp2 %>% regress_wt1(outcome_var)
  tmp2 %>% regress_wt3(outcome_var)
  tmp2 %>% regress_wt4(outcome_var)
  
  # Unweighted - Non-MJ States
  tmp2 %>% filter(mjstate == 0) %>% regress_0(outcome_var)
  tmp2 %>% filter(mjstate == 0) %>% regress_1(outcome_var)
  tmp2 %>% filter(mjstate == 0) %>% regress_3(outcome_var)
  tmp2 %>% filter(mjstate == 0) %>% regress_4(outcome_var)
  
  # Weighted - Non-MJ States
  tmp2 %>% filter(mjstate == 0) %>% regress_wt0(outcome_var)
  tmp2 %>% filter(mjstate == 0) %>% regress_wt1(outcome_var)
  tmp2 %>% filter(mjstate == 0) %>% regress_wt3(outcome_var)
  tmp2 %>% filter(mjstate == 0) %>% regress_wt4(outcome_var)
  
  # Unweighted - MJ States
  tmp2 %>% filter(mjstate == 1) %>% regress_0(outcome_var)
  tmp2 %>% filter(mjstate == 1) %>% regress_1(outcome_var)
  tmp2 %>% filter(mjstate == 1) %>% regress_3(outcome_var)
  tmp2 %>% filter(mjstate == 1) %>% regress_4(outcome_var)
  
  # Weighted - MJ States
  tmp2 %>% filter(mjstate == 1) %>% regress_wt0(outcome_var)
  tmp2 %>% filter(mjstate == 1) %>% regress_wt1(outcome_var)
  tmp2 %>% filter(mjstate == 1) %>% regress_wt3(outcome_var)
  tmp2 %>% filter(mjstate == 1) %>% regress_wt4(outcome_var)
}

```

