---
title: "NSDUH Substance Use Disorders"
output: 
  html_document:
   theme: paper 
   toc: true
   toc_float: true
---

```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE)

library(tidyverse)
library(gtsummary)
library(survey)
```

```{r, eval = FALSE}
# source("PolicyDataset.R")
```

```{r}
temp <- readRDS("Temp020525.RDA")
```

Setup Files 

```{r}
source("PolicyLabels.R")
```

Load Dataset

```{r message = FALSE, warning=FALSE}

temp2 <- temp %>% haven::zap_labels() 


# Adds Simulated Region !!! NOT FOR USE!!! 
df <- tibble(region_1 = 1:4)
region_d <- sample_n(df, length(temp2$year), replace = TRUE)

temp2 <- bind_cols(temp2, region_d)

grp_ <- temp2  %>% filter(!catag6=="") %>% filter(!year == 2020) %>% droplevels()

grp1 <- temp2 %>% filter(year > 2020) %>% filter(!catag6 == "")
grp2 <- temp2 %>% filter(year < 2020) %>% filter(!catag6 == "")

desg_ <-
  temp2 %>% haven::zap_labels() %>% filter(!catag6=="") %>% droplevels() %>%
  svydesign(id      = ~verep,
            strata  = ~vestr_,
            weights = ~psnwt,
            data    = . , nest = T)


desg_1 <-
  temp2 %>% haven::zap_labels() %>% filter(!catag6=="") %>% filter(year < 2020) %>%  droplevels()  %>%
  svydesign(id      = ~verep,
            strata  = ~vestr_,
            weights = ~psnwt,
            data    = . , nest = T)


desg_2 <-
  temp2 %>% haven::zap_labels() %>% filter(!catag6=="") %>% filter(year > 2020) %>% droplevels() %>%
  svydesign(id      = ~verep,
            strata  = ~vestr_,
            weights = ~psnwt,
            data    = . , nest = T)
```

```{r}
# Generate a freq plot by year

generate_plot <- function(data, outcome, title) {
  total <- data %>% filter(!!sym(outcome) == "Positive" | !!sym(outcome) == 1) %>% nrow()
  data %>%
    group_by(!!sym(outcome), year) %>%
    tally() %>%
    filter(!!sym(outcome) == "Positive" | !!sym(outcome) == 1 ) %>%
    droplevels() %>%
    ggplot(aes(y = n, x = year)) +
    geom_col(width = 0.5, fill = "steelblue") +
    theme_bw() +
    labs(y = "Number of Respondents", x = "Year", title = paste(title, "- Total:", total))
}

tbl1covariates = c("period_indic", "catag6", "irsex", "race_cat", 
                   "irmarit", "eduhighcat", "irwrkstat", "income", "rskyfqtes", 
                   "halluc_p",
                   "mj_ever", "trq_ever", "inh_ever", "ecstasy_ever", "pcp_ever","sed_ever","coc_ever", "meth_ever", 
                   "difobther", "difobtlsd")

tbl1_unweighted <- function(data, outcome) {
  data %>%
    tbl_summary(
      include = all_of(tbl1covariates),
      by = all_of(outcome),
      percent = "column",
      label = c( demo_var_list, outcome_list_label, substance_list_label) 
    ) %>% modify_header(label =  "Variable")
}

tbl1_weighted <- function(design, outcome) {
  design %>%
    tbl_svysummary(
      include = all_of(tbl1covariates),
      by = all_of(outcome),
      percent = "column",
      label = c(demo_var_list,  outcome_list_label, substance_list_label)
    ) %>% add_overall() %>% add_p() %>% modify_header(label =  "Variable")
}
```

# Substance Reference

- Heroin  
- Pain Relievers
- Any Opioid Use
- Cannabis
- Ketamine
- MDMA
- Methamphetamine
- Cocaine
- Stimulants
- CUPS Hallucinogens
- Tranquilizers
- PCP
- Inhalants
- Sedatives

```{r}
substance_list <- c("halluc_p", "lsd_ever", "psilcy_ever", "ecstasy_ever", "ket_ever", "pcp_ever", "mesc_ever","peyote_ever","dmt_ever", "salv_ever","mj_ever", "coc_ever", "meth_ever", "stm_ever", "trq_ever", "inh_ever", "sed_ever", "herflag", "pnranyflag", "any_opi")

reference_summary <- function(data) {
  data %>%
  tbl_summary(
    include = all_of(substance_list),
    percent = "column",
    by = "year",
    label = c(outcome_list_label, substance_list_label)
  )
}

grp_ %>% reference_summary()

# grp1 %>% reference_summary()
# grp2 %>% reference_summary()

```

# Opioid Use Disorder

### Frequency Plot 

```{r}
generate_plot(temp2, "opioid_use_f", "Opioid Use Disorder")
```

### Demographics by Opioid Use Disorder 

```{r, eval = FALSE}
# Unweighted for Adult Respondents
grp_ %>%
  tbl_summary(include = all_of(tbl1covariates),
                 by = "opioid_use_f",
                 percent = "column",
                 label = demo_var_list)

# Weighted for All Respondents

desg_ %>% 
  tbl_svysummary(
      include = all_of(tbl1covariates),
      by = "opioid_use_f",
      percent = "column", 
      label = demo_var_list
    ) %>% add_overall()

rm(temp, region_d, df)
```

```{r}
tbl1_unweighted(grp_, "opioid_use_f")
tbl1_weighted(desg_, "opioid_use_f")
```

### Models

```{r model_definitions}
ud_regress <- function(substance, datsrc) {
  formula <- as.formula(paste("opioid_use ~", substance))
#Perform logistic regression using the glm function with binomial family
 glm(data = datsrc, formula, family = "binomial") %>% 
   tbl_regression(exponentiate = TRUE,
                  label = c(demo_var_list, substance_list_label))
}

ud_regress_a <- function(substance) {
  formula <- as.formula(paste("opioid_use ~", substance))
  # Perform Weighted logistic regression using the svyglm function with binomial family
  svyglm(design = desg_2, 
        formula = formula, family = "binomial")  %>% 
    tbl_regression(exponentiate = TRUE,
                  label = c(demo_var_list, substance_list_label))
}

ud_regress_b <- function(substance) {
  formula <- as.formula(paste("opioid_use ~", substance))
  # Perform Weighted logistic regression using the svyglm function with binomial family
  svyglm(design = desg_1, 
        formula = formula, family = "binomial")  %>% 
    tbl_regression(exponentiate = TRUE,
                  label = c(demo_var_list, substance_list_label))
}

# New Regression function that works for all substances
use_regress_a = function(dependent ,substance) {
  formula = as.formula(paste(dependent, " ~", substance))
  svyglm(design = desg_2, formula = formula, family = "binomial") %>% 
    tbl_regression(exponentiate = TRUE, label = c(demo_var_list, substance_list_label))
}

 use_regress_b = function(dependent ,substance) {
  formula = as.formula(paste(dependent, " ~", substance))
  svyglm(design = desg_1, formula = formula, family = "binomial") %>% 
    tbl_regression(exponentiate = TRUE, label = c(demo_var_list, substance_list_label))
}
```

Model 0 

(Unweighted/Unadjusted Table)

```{r}
obj0 = lapply(substance_list[1:18], ud_regress, datsrc = grp_ )


unadj_temp = bind_rows(lapply(obj0, function(x) x$table_body)) %>% 
  select(N_event, var_label, N_obs, estimate, ci, p.value)

unadj_temp %>% 
  select(Var = var_label, Estimate = estimate, CI = ci, p = p.value) %>% 
  knitr::kable(digits = 3)

rm(obj0, unadj_temp)

```

(Classic Hallucinogens ~ Weighted)

```{r, warning=FALSE}
# 2015 - 2019
ud_regress_b("halluc_p")

# 2020 - 2022
ud_regress_a("halluc_p")

m1vars = "catag6 + race_cat + income + irsex + eduhighcat + mj_ever + stm_ever+ trq_ever + inh_ever + sed_ever + coc_ever + meth_ever"
m2vars = str_c(m1vars, " + difobtlsd + difobther")
m3vars = str_c(m1vars, " + factor(region_1)")

m1varsmj = "catag6 + race_cat + income + irsex + eduhighcat + stm_ever+ trq_ever + inh_ever + sed_ever + coc_ever + meth_ever"
m2varsmj = str_c(m1varsmj, " + difobtlsd + difobther")

psyvars = "psilcy_ever + peymesc + lsd_ever + dmt_ever"

```

Model 1

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use* 

```{r, warning = F}

# 2015 - 2019
ud_regress_b(paste("halluc_p" ," + "  , m1vars))

# 2020 - 2022
ud_regress_a(paste("halluc_p" ," + "  , m1vars))

# 2015 - 2019
ud_regress_b(paste(psyvars, " + "  , m1vars))

# 2020 - 2022
ud_regress_a(paste(psyvars, " + "  , m1vars))
```

Model 2 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Difficulty Obtaining* 

```{r}

# 2015 - 2019
ud_regress_b(paste("halluc_p" ," + "  , m2vars))

# 2020 - 2022
ud_regress_a(paste("halluc_p" ," + "  , m2vars))

# 2015 - 2019
ud_regress_b(paste(psyvars ," + "  , m2vars))

# 2020 - 2022
ud_regress_a(paste(psyvars ," + "  , m2vars))
```

Model 3 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Geo Region* 

```{r, eval = FALSE }
# 2015 - 2019
ud_regress_b(paste("halluc_p" ," + "  , m3vars))

# 2020 - 2022
ud_regress_a(paste("halluc_p" ," + "  , m3vars))

# 2015 - 2019
ud_regress_b(paste(psyvars ," + "  , m3vars))

# 2020 - 2022
ud_regress_a(paste(psyvars ," + "  , m3vars))
```

Model 4 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Policy 2019/2023* 

```{r, eval = FALSE }
# 2015 - 2019
ud_regress_b(paste("halluc_p" ," + "  , m1vars, " + " , policy19))

# 2020 - 2022
ud_regress_a(paste("halluc_p" ," + "  , m1vars, " + ",  policy23))

# 2015 - 2019
ud_regress_b(paste(psyvars ," + "  , m1vars, " + " , policy19))

# 2020 - 2022
ud_regress_a(paste(psyvars ," + "  , m1vars, " + ",  policy23))
```

# Other Past Year Substance Use

## Past Year Cannabis Use

### Frequency Plot 

```{r}
generate_plot(temp2, "mrjyr", "Past Year Cannabis Use")
```

### Demographics by PY Cannabis Use
 
```{r}
tbl1_unweighted(grp_, "mrjyr")
tbl1_weighted(desg_, "mrjyr")
```
 
### Models

(Classic Hallucinogens ~ Weighted)

```{r}
# 2015 - 2019
use_regress_b("mrjyr", paste("halluc_p"))

# 2020 - 2022
use_regress_a("mrjyr", paste("halluc_p"))
```

Model 1

```{r}
use_regress_b("mrjyr", paste("halluc_p", " + ", m1varsmj))
use_regress_a("mrjyr", paste("halluc_p", " + ",  m1varsmj))
```

Model 2 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Difficulty Obtaining* 

```{r}

# 2015 - 2019
use_regress_b("mrjyr", paste("halluc_p", " + ", m2varsmj))

# 2020 - 2022
use_regress_a("mrjyr", paste("halluc_p", " + ", m2varsmj))
```

Model 3 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Geo Region* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("mrjyr", paste("halluc_p", " + ", m3varsmj))

# 2020 - 2022
use_regress_a("mrjyr", paste("halluc_p", " + ", m3varsmj))

```

Model 4

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Policy 2019/2023* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("mrjyr", paste("halluc_p", " + ", m1varsmj, " + ", policy19))

# 2020 - 2022
use_regress_a("mrjyr", paste("halluc_p", " + ", m1varsmj, " + ", policy23))
```


## Past Year Ketamine Use

### Frequency Plot 

```{r}
generate_plot(temp2, "ketminyr", "Past Year Ketamine Use")
# generate_plot(temp2, "ket_ever" , "Ketamine Use")
```

### Demographics by PY Ketamine Use

```{r}
tbl1_unweighted(grp_, "ketminyr")
tbl1_weighted(desg_, "ketminyr")
```

### Models

Model 1

```{r}
use_regress_b("ketminyr", paste("halluc_p", " + ", m1vars))
use_regress_a("ketminyr", paste("halluc_p", " + ", m1vars))
```

Model 2 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Difficulty Obtaining* 

```{r}
# 2015 - 2019
use_regress_b("ketminyr", paste("halluc_p", " + ", m2vars))

# 2020 - 2022
use_regress_a("ketminyr", paste("halluc_p", " + ", m2vars))
```

Model 3 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Geo Region* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("ketminyr", paste("halluc_p", " + ", m3vars))

# 2020 - 2022
use_regress_a("ketminyr", paste("halluc_p", " + ", m3vars))

```

Model 4

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Policy 2019/2023* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("ketminyr", paste("halluc_p", " + ", m1vars, " + ", policy19))

# 2020 - 2022
use_regress_a("ketminyr", paste("halluc_p", " + ", m1vars, " + ", policy23))
```

## Past Year MDMA Use

```{r}
generate_plot(temp2, "ecstmoyr", "Past Year MDMA Use")
```

### Demographics by PY MDMA Use  
```{r}
tbl1_unweighted(grp_, "ecstmoyr")
tbl1_weighted(desg_,"ecstmoyr")
```

### Models


(Classic Hallucinogens ~ Weighted)

```{r}
# 2015 - 2019
use_regress_b("ecstmoyr", paste("halluc_p"))

# 2020 - 2022
use_regress_a("ecstmoyr", paste("halluc_p"))
```


Model 1

```{r}
use_regress_b("ecstmoyr", paste("halluc_p", " + ", m1vars))
use_regress_a("ecstmoyr", paste("halluc_p", " + ", m1vars))
```

Model 2 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Difficulty Obtaining* 

```{r}

# 2015 - 2019
use_regress_b("ecstmoyr", paste("halluc_p", " + ", m2vars))

# 2020 - 2022
use_regress_a("ecstmoyr", paste("halluc_p", " + ", m2vars))
```

Model 3 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav, Lifetime Drug Use + Geo Region* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("ecstmoyr", paste("halluc_p", " + ", m3vars))

# 2020 - 2022
use_regress_a("ecstmoyr", paste("halluc_p", " + ", m3vars))

```

Model 4

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav, Lifetime Drug Use + Policy 2019/2023* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("ecstmoyr", paste("halluc_p", " + ", m1vars, " + ", policy19))

# 2020 - 2022
use_regress_a("ecstmoyr", paste("halluc_p", " + ", m1vars, " + ", policy23))
```

## Past Year Non Prescribed Stimulant Use

### Frequency Plot 

```{r}
generate_plot(temp2, "py_cocmeth" , "Past Year Non Prescribed Stimulant Use")
```

### Demographics by PY Non Prescribed Stimulant Use
```{r}
tbl1_unweighted(grp_, "py_cocmeth")
tbl1_weighted(desg_, "py_cocmeth")
```

### Models

(Classic Hallucinogens ~ Weighted)

```{r}
# 2015 - 2019
use_regress_b("py_cocmeth", paste("halluc_p"))
# 2020 - 2022
use_regress_a("py_cocmeth", paste("halluc_p"))
```


Model 1

```{r}
use_regress_b("py_cocmeth", paste("halluc_p", " + ", m1vars))
use_regress_a("py_cocmeth", paste("halluc_p", " + ", m1vars))
```

Model 2 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Difficulty Obtaining* 

```{r}
# 2015 - 2019
use_regress_b("py_cocmeth", paste("halluc_p", " + ", m2vars))

# 2020 - 2022
use_regress_a("py_cocmeth", paste("halluc_p", " + ", m2vars))
```

Model 3 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Geo Region* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("py_cocmeth", paste("halluc_p", " + ", m3vars))

# 2020 - 2022
use_regress_a("py_cocmeth", paste("halluc_p", " + ", m3vars))

```

Model 4

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Policy 2019/2023* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("py_cocmeth", paste("halluc_p", " + ", m1vars, " + ", policy19))

# 2020 - 2022
use_regress_a("py_cocmeth", paste("halluc_p", " + ", m1vars, " + ", policy23))
```


# Other Past Year Use Disorders

## Alcohol Use Disorder 

### Frequency Plot 

```{r}
generate_plot(temp2, "alc_use_f" , "Past Year Alcohol Use Disorder")
```

### Demographics by Alcohol Use Disorder

```{r}
tbl1_unweighted(grp_, "alc_use_f")
tbl1_weighted(desg_,"alc_use_f")
```

### Models

(Classic Hallucinogens ~ Weighted)

```{r}
# 2015 - 2019
use_regress_b("alc_use_f", paste("halluc_p"))

# 2020 - 2022
use_regress_a("alc_use_f", paste("halluc_p"))
```

Model 1

```{r}
use_regress_b("alc_use_f", paste("halluc_p", " + ", m1vars))
use_regress_a("alc_use_f", paste("halluc_p", " + ", m1vars))
```

Model 2 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Difficulty Obtaining* 

```{r}

# 2015 - 2019
use_regress_b("alc_use_f", paste("halluc_p", " + ", m2vars))

# 2020 - 2022
use_regress_a("alc_use_f", paste("halluc_p", " + ", m2vars))
```

Model 3 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Geo Region* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("alc_use_f", paste("halluc_p", " + ", m3vars))

# 2020 - 2022
use_regress_a("alc_use_f", paste("halluc_p", " + ", m3vars))

```

Model 4

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Policy 2019 /2023* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("alc_use_f", paste("halluc_p", " + ", m1vars, " + ", policy19))

# 2020 - 2022
use_regress_a("alc_use_f", paste("halluc_p", " + ", m1vars, " + ", policy23))
```

## Binge Alcohol use past 30 days 

### Frequency Plot 

```{r}
generate_plot(temp2, "binge_drink" , "Past Year Alcohol Use Disorder")
```

### Demographics by Binge Alcohol use past 30 days 

```{r}
tbl1_unweighted(grp_, "binge_drink_f")
tbl1_weighted(desg_,"binge_drink_f")
```

### Models

(Classic Hallucinogens ~ Weighted)

```{r}
# 2015 - 2019
use_regress_b("binge_drink_f", paste("halluc_p"))

# 2020 - 2022
use_regress_a("binge_drink_f", paste("halluc_p"))
```

Model 1

```{r}
use_regress_b("binge_drink_f", paste("halluc_p", " + ", m1vars))
use_regress_a("binge_drink_f", paste("halluc_p", " + ", m1vars))
```

Model 2 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Difficulty Obtaining* 

```{r}

# 2015 - 2019
use_regress_b("binge_drink_f", paste("halluc_p", " + ", m2vars))

# 2020 - 2022
use_regress_a("binge_drink_f", paste("halluc_p", " + ", m2vars))
```

Model 3 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Geo Region* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("binge_drink_f", paste("halluc_p", " + ", m3vars))

# 2020 - 2022
use_regress_a("binge_drink_f", paste("halluc_p", " + ", m3vars))

```

Model 4

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Policy 2019 /2023* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("binge_drink_f", paste("halluc_p", " + ", m1vars, " + ", policy19))

# 2020 - 2022
use_regress_a("binge_drink_f", paste("halluc_p", " + ", m1vars, " + ", policy23))
```

## Non Prescribed Stimulant Use Disorder 
(Methaphetamine + Cocaine)

### Frequency Plot 

```{r}
generate_plot(temp2, "cocmeth_use_f", "Past Year Non Prescribed Stimulant Use Disorder")
```

### Demographics by Non Prescribed Stimulant Use Disorder
(Methaphetamine + Cocaine)

```{r}
tbl1_unweighted(grp_, "cocmeth_use_f")
tbl1_weighted(desg_,"cocmeth_use_f")
```

### Models

(Classic Hallucinogens ~ Weighted)

```{r}
# 2015 - 2019
use_regress_b("cocmeth_use_f", paste("halluc_p"))

# 2020 - 2022
use_regress_a("cocmeth_use_f", paste("halluc_p"))
```

Model 1

```{r}
use_regress_b("cocmeth_use_f", paste("halluc_p", " + ", m1vars))
use_regress_a("cocmeth_use_f", paste("halluc_p", " + ", m1vars))
```

Model 2 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Difficulty Obtaining* 

```{r}

# 2015 - 2019
use_regress_b("cocmeth_use_f", paste("halluc_p", " + ", m2vars))

# 2020 - 2022
use_regress_a("cocmeth_use_f", paste("halluc_p", " + ", m2vars))
```

Model 3 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Geo Region* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("cocmeth_use_f", paste("halluc_p", " + ", m3vars))

# 2020 - 2022
use_regress_a("cocmeth_use_f", paste("halluc_p", " + ", m3vars))

```

Model 4

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Policy 2019 /2023* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("cocmeth_use_f", paste("halluc_p", " + ", m1vars, " + ", policy19))

# 2020 - 2022
use_regress_a("cocmeth_use_f", paste("halluc_p", " + ", m1vars, " + ", policy23))
```

## Cannabis Use Disorder 

### Frequency Plot 

```{r}
generate_plot(temp2, "mrj_use_f" , "Past Year Cannabis Use Disorder")
```

### Demographics by Cannabis Use Disorder

```{r}
tbl1_unweighted(grp_, "mrj_use_f")
tbl1_weighted(desg_, "mrj_use_f")
```

### Models

(Classic Hallucinogens ~ Weighted)

```{r}
# 2015 - 2019
use_regress_b("mrj_use_f", paste("halluc_p"))
# 2020 - 2022
use_regress_a("mrj_use_f", paste("halluc_p"))
```

Model 1

```{r}
use_regress_b("mrj_use_f", paste("halluc_p", " + ", m1varsmj))
use_regress_a("mrj_use_f", paste("halluc_p", " + ", m1varsmj))
```

Model 2 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Difficulty Obtaining* 

```{r}

# 2015 - 2019
use_regress_b("mrj_use_f", paste("halluc_p", " + ", m2varsmj))

# 2020 - 2022
use_regress_a("mrj_use_f", paste("halluc_p", " + ", m2varsmj))
```

Model 3 

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Geo Region* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("mrj_use_f", paste("halluc_p", " + ", m3varsmj))

# 2020 - 2022
use_regress_a("mrj_use_f", paste("halluc_p", " + ", m3varsmj))

```

Model 4

*Control Vars: Age, Sex Income, Race, Education, Employment, RiskyBehav , Lifetime Drug Use + Policy 2019/2023* 

```{r, eval = FALSE }

# 2015 - 2019
use_regress_b("mrj_use_f", paste("halluc_p", " + ", m1varsmj, " + ", policy19))

# 2020 - 2022
use_regress_a("mrj_use_f", paste("halluc_p", " + ", m1varsmj, " + ", policy23))
```

## Notes

OUD	Past year opioid use disorder 
  (UDPYOPI and UD5OPIANY) 
	
Ketamine
  Past year use (KETAYRR)
  
MDMA
  Past year use (ECSTMOYR)
  
Alcohol
  Past year AUD (ABODALC and PYUD5ALC)
  
Methamphetamine + Cocaine 
 	Past year use (COCYR + METHAMYR)

Past year stimulant use disorder 
	      (ABODCOC + UDPYMTH and PYUD5COC + PYUD5MTH)
Cannabis:	
  Past year use (MRJYR)
	Past year cannabis use disorder (ABODMRJ and PYUD5MRJ)
	
** NEW ** Past month binge drinking	(BNGDRNKMON)


```{r, message = FALSE, warning = FALSE, eval = FALSE}
grp1 %>% haven::zap_labels() %>%
  tbl_summary(include = c("opioid_use_f") ,
                 percent = "column", by = "region_1",
              label = list(opioid_use_f = "Opioid Use Disorder")) %>%
                 # add_overall() %>% 
  modify_header(label =  "Variable") %>% 
  modify_caption("**Distribution of Outcomes by Region**") %>% 
  modify_footnote(all_stat_cols() ~ NA)

grp1 %>%
  tbl_summary(
    include = c(psilcy_ever,
                halluc_p, lsd_ever, ecstasy_ever, ket_ever, pcp_ever, mesc_ever, dmt_ever, salv_ever, meth_ever,
                herflag , pnranyflag, any_opi ),
    by = "year",
    percent = "column",
    label = c( outcome_list_label, substance_list_label)
      )

grp2 %>%
  tbl_summary(
    include = c(psilcy_ever,
                halluc_p, lsd_ever, ecstasy_ever, ket_ever, pcp_ever, mesc_ever, dmt_ever, salv_ever, meth_ever,
                herflag , pnranyflag, any_opi ),
    by = "year",
    percent = "column",
    label = c( outcome_list_label, substance_list_label)
      )

# List of substances to analyze
substances <- c("halluc_p", "psilcy_ever", 
                "lsd_ever", "mesc_ever","ecstasy_ever", "peyote_ever", 
                "mj_ever", "coc_ever", "trq_ever", "pcp_ever", "sed_ever", "stm_ever", "inh_ever", "meth_ever",
                "dmt_ever" 
                )

```

Unweighted 

```{r eval=FALSE, include=FALSE}
grp_  %>% haven::zap_labels() %>%
  tbl_summary(
    include= c( 
    "halluc_ever", 
    "lsd_ever","psilcy_ever", "mj_ever", "coc_ever", "meth_ever"),
    by = opioid_use_f,
    label = c(outcome_list_label, substance_list_label),
    percent = "column")
```

```{r, eval = FALSE, message = FALSE, warning = FALSE}
# Hallucinogens 
temp2 %>% 
  tbl_summary(
    include = c(opioid_use, pain_use, her_use, psilcy_ever, halluc_p, pnranyflag, herflag
                # , any_opi
                ),
    by = "year",
    percent = "column", 
    label = outcome_list_label
    )

temp2 %>%
  tbl_summary(
    include = c(psilcy_ever,
                halluc_p, lsd_ever,  ecstasy_ever, ket_ever, pcp_ever, mesc_ever, dmt_ever,salv_ever),
    by = "year",
    percent = "column",
    label = c( outcome_list_label, substance_list_label)
      )

temp2 %>%
  tbl_summary(
    include = c(mj_ever, coc_ever, stm_ever, trq_ever, inh_ever,sed_ever),
    by = "year",
    label = substance_list_label,
    percent = "column")
```

```{r, eval = FALSE, message = FALSE, warning = FALSE}

### Weighted Demographics by Classic Psychedelic Use (Adult Opioid Ever Users)

desg3_ %>% 
     update( 
        . , 
        halluc_p = 
            factor( 
                halluc_p , 
                levels = 0:1 , 
                labels = c("Never Used", "Ever Used")
            )) %>% 
  tbl_svysummary(include = 
                    c("year", "catag6","irsex", "race_cat", "irmarit", "eduhighcat", "irwrkstat", "income", 
                      "rskyfqtes", "difobther", "difobtlsd",
                      "opioid_use_f"
                      # , "any_opi","pnranyflag","herflag"
                      ),
                 by = 'halluc_p', 
                 percent = "column",
                 label = c(demo_var_list, irhallucrec = "NSDUH Hallucinogen Recency", race_cat = "Race/Ethnicity", 
                           outcome_list_label)
                   ) %>% add_overall(last = T) %>% add_p() %>% 
  modify_header(label =  "Variable") %>% 
  modify_caption("**Weighted Frequency by Classic Psychedelic Use**")

desg3_ %>% 
     update( 
        . , 
        
        halluc_p = 
            factor( 
                halluc_p , 
                levels = 0:1 , 
                labels = c("Never Use", "Ever Used")
            )) %>% 
  tbl_svysummary(include = 
                    c("mj_ever", "trq_ever", "inh_ever", "ecstasy_ever", "pcp_ever", "sed_ever", "coc_ever", "meth_ever"),
                 by = 'halluc_p', 
                 percent = "row",
                 label = c(substance_list_label)
                   ) %>% 
  add_overall(last = T) %>% add_p() %>% 
  modify_header(label =  "Variable") %>% 
  modify_caption("**Weighted Frequency by Classic Psychedelic Use**") 
```